Self Regulation Ontology Retest Data Report

### 2018-02-19 code/SRO_Report.Rmd
updating report w new data

```{r}
boot_df
```

>>>>

Which variables have significant time effects in more than 5% of the bootstrapped samples?

22/74 survey measures
135/335 task measures

```{r}
boot_df %>%
  select(dv, p_time, task) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect)
```
